Bayes Optimal Informer Sets for Drug Discovery\thanks{abc}

### 2020-06-08 BOISE/Paper_draft/draft.tex
Draft Update

\subsubsection{Retrospective Results}
We conduct retrospective leave one out cross validation for each one of $224$ PKIS1 targets. For BOISE, we use the informer size $n_A = 8$ as it is quite computational intensive. For Accelerated-BOISE, both $n_A= 8$ and $n_A = 16$ are used to compare different methods. Results from $224$ separate experiments are summarized in violin plots.

When informer set size $n_A = 8$, Figure \ref{fig:pkis8} summarize cross validation results with respect to NEF10 and ROCAUC metrics. From pairwise tests, we can see that BOISE and Accelerated-BOISE are both significantly better than other baseline and non-baseline methods, and BOISE performs similarly to Accelerated-BOISE. Although BOISE is still slightly better than Accelerated-BOISE overall, as it is optimal theoretically, their difference is not statically significant. 
To be more specific, it can be seen from Figure \ref{fig:pkis8} that Adaptive Selection (AS8) is the best method other than (AC-)BOISE8 under NEF10 metric. From paired t-test between AS8 and (AC-)BOISE8, the mean difference between BOISE8 and AS8 is $0.0608$, with p-value $<2.2\times 10^{-16}$; the mean difference between AC-BOISE8 and AS8 is $0.0520$, with p-value $=6.466\times 10^{-14}$. Similarly, Coding Selection (CS8) is the best method other than (AC-)BOISE8 under ROCAUC. The mean difference between BOISE8 and CS8 is $0.0283$, with p-value $=3.73\times 10^{-6}$ and the mean difference between AC-BOISE8 and CS8 is $0.0258$, with p-value $=3.035\times 10^{-5}$.

@@

Same thing happens when we boost informer set size from $n_A = 8$ to $16$. Since BOISE takes too much time for a leave-one-out cross validation under $n_A=16$, we can not afford it, instead we treat Accelerated-BOISE as a lower bound of BOISE performance as Figure \ref{fig:pkis8} tell us. Empirical results summarized in Figure \ref{fig:pkis16} show that AC-BOISE is still significantly better than previous methods: Under NEF10 metric, Adaptive Selection (AS16) is the best method other than AC-BOISE and the paired t-test shows that their mean difference is $0.0415$ with p-value $=6.199\times 10^{-7}$;  Under ROCAUC metric, Regression Selection (RS16) is the best method other than AC-BOISE and the paired t-test shows that their mean difference is $0.0294$ with p-value $=1.303\times 10^{-4}$. 
\begin{figure}[!ht]
\centering
\includegraphics[width=5.0in]{PKIS1_16_eval.png}
\caption{\label{fig:pkis16} 
{\bf Violin plot comparison of different methods under informer size $n_A =16$ with respect to compound ranking performance assessed by NEF10 and ROCAUC.}}
\end{figure}

@@

In figures \ref{fig:gdsc} we show that BOISE and AC-BOISE are still better than previous methods on the new GDSC data set, with informer size $n_A = 8$ and $n_A = 16$. In particular, Adaptive Selection (AS8 and AS16) is the best method other than BOISE and AC-BOISE. When $n_A = 8$, paired t-test shows that the mean difference in NEF10 between BOISE8 and AS8 is $0.0315$ with p-value $= 1.743\times 10^{-4}$; the mean difference in ROCAUC between BOISE8 and AS8 is $0.0493$ with p-value $= 3.756\times 10^{-10}$; When $n_A = 16$, paired t-test shows that the mean difference in NEF10 between AC-BOISE16 and AS16 is $0.0352$ with p-value $= 2.908\times 10^{-6}$; the mean difference in ROCAUC between AC-BOISE16 and AS16 is $0.0682$ with p-value $<2.2\times 10^{-16}$.

>>>>

\subsubsection{Retrospective Results}
We conduct retrospective leave one out cross validation for each one of $224$ PKIS1 targets. Informer size of $n_A= 8$ and $n_A = 16$ are applied to compare performance of different methods under different informer size settings. Results from $224$ separate experiments are summarized in violin plots.

When informer set size $n_A = 8$, Figure \ref{fig:pkis8} summarizes cross validation results with respect to NEF10 and ROCAUC metrics. From pairwise tests, we can see that BOISE and Accelerated-BOISE are both significantly better than other baseline and non-baseline methods, and BOISE performs similarly to Accelerated-BOISE. Although BOISE is still slightly better than Accelerated-BOISE overall, as it is optimal theoretically, their difference is not statically significant. 
To be more specific, it can be seen from Figure \ref{fig:pkis8} that Adaptive Selection (AS8) is the best method other than (AC-)BOISE8 under NEF10 metric. From paired t-test between AS8 and (AC-)BOISE8, the mean difference between BOISE8 and AS8 is $0.0608$, with p-value $<2.2\times 10^{-16}$; the mean difference between AC-BOISE8 and AS8 is $0.0520$, with p-value $=6.466\times 10^{-14}$. Similarly, Coding Selection (CS8) is the best method other than (AC-)BOISE8 under ROCAUC. The mean difference between BOISE8 and CS8 is $0.0283$, with p-value $=3.73\times 10^{-6}$ and the mean difference between AC-BOISE8 and CS8 is $0.0258$, with p-value $=3.035\times 10^{-5}$.

@@

Same thing happens when we boost informer set size from $n_A = 8$ to $16$. We rely on distributed computing offered by CHTC to complete this cross validation as BOISE will take a lot of time on personal computer. Empirical results summarized in Figure \ref{fig:pkis16} show that BOISE and AC-BOISE are still significantly better than previous methods: Under NEF10 metric, Adaptive Selection (AS16) is the best method other than (AC-)BOISE and the paired t-test shows that the mean difference between BOISE and AS is $0.0421$ with p-value $=6.115\times 10^{-7}$;  Under ROCAUC metric, Regression Selection (RS16) is the best method other than (AC-)BOISE and the paired t-test shows that the mean difference between BOISE and RS is $0.0294$ with p-value $=1.303\times 10^{-4}$. 
\begin{figure}[!ht]
\centering
\includegraphics[width=5.0in]{PKIS1_16_eval.png}
\caption{\label{fig:pkis16} 
{\bf Violin plot comparison of different methods under informer size $n_A =16$ with respect to compound ranking performance assessed by NEF10 and ROCAUC.}}
\end{figure}

@@

In figures \ref{fig:gdsc} we show that BOISE and AC-BOISE are better than previous methods on the new GDSC data set, with informer size $n_A = 8$ and $n_A = 16$. In particular, Adaptive Selection (AS8 and AS16) is the best method other than (AC-)BOISE. When $n_A = 8$, paired t-test shows that the mean difference in NEF10 between BOISE8 and AS8 is $0.0315$ with p-value $= 1.743\times 10^{-4}$; the mean difference in ROCAUC between BOISE8 and AS8 is $0.0493$ with p-value $= 3.756\times 10^{-10}$; When $n_A = 16$, paired t-test shows that the mean difference in NEF10 between BOISE16 and AS16 is $0.0448$ with p-value $= 2.837\times 10^{-8}$; the mean difference in ROCAUC between AC-BOISE16 and AS16 is $0.0781$ with p-value $<2.2\times 10^{-16}$.
